---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# robinhood

[Robinhood](https://robinhood.com/company/) is here to democratize access to the financial markets. This is an R package to help with that.

This package is made based on the [unofficial documentation](https://github.com/sanko/Robinhood/) so it might have a few rough edges.

I have only implemented the parts of the API where authentication isn't needed, since I can't open an account. Please feel free to add the missing functionality.

### Issues

- The time zones are still a bit of a mystery to me, which is why I've just used UTC for now.
- All the requests that require authentication are not implemnted.

### Current functionality

- Get the last quote: (`rh_quote`)
- Historical quotes: (`rh_historicals`)
- Meta info on markets: (`rh_markets`)
- Get the market hours for a specific market: (`rh_market_hours`)
- Get all the instruments (the api returns paginated results, so it might take a while to download): (`rh_instruments`)
- Instruments fundamentals: (`rh_instruments_info`)
- Instruments splits: (`rh_instruments_split`)
- instruments keyword search: (`rh_instruments_search`)

### A few examples

Let's see how it works. Load the package and set the symbols.

```{r getready, message=FALSE}

library(robinhoodr)
library(quantmod)

symbols <- c("MSFT", "FB")

```

#### Historical data


Let's get some intraday data. The query below returns a list of length two with xts objects.

The function will make a request to the API for each individual symbol, soo if there are many symbols it can take a while.

```{r intrahist}

hd <- rh_historicals(symbols = symbols, 
                     interval = "5minute", 
                     span = "day", 
                     bounds = "regular", 
                     keep_meta = FALSE, 
                     to_xts = TRUE)

str(hd)

```

Use quantmod to plot the Microsoft data.

```{r printmsft}

print(chart_Series(x = hd[["MSFT"]]))

```

You can't get more than a years worth of historical data. I don't know if [Robinhood](https://support.robinhood.com/hc/en-us/articles/210216823-Robinhood-API-Integrations) might change that. In the example below a list with data frames are returned.

```{r dailydata}

hd_daily <- rh_historicals(symbols = symbols, 
                           interval = "day", 
                           span = "year", 
                           bounds = "regular", 
                           to_xts = FALSE)

str(hd_daily)

```

You can decide to keep the meta data from the API request but only if the nested historical data is a data.frame.

```{r dailydatawithmeta}

hd_daily <- rh_historicals(symbols = symbols, 
                           interval = "day", 
                           span = "year", 
                           bounds = "regular", keep_meta = TRUE, to_xts = FALSE)

str(hd_daily)

```

### Quotes

Get the latest quote.

```{r getquote}

str(rh_quote(symbols = symbols))

```


#### Markets

Get info on the markets. The last time I looked it up there were about 14 exchanges, so this must be the exchanges Robinhood use to execute the transactions. 

```{r markets}

# List markets
str(rh_markets())

# Get specific market info
str(rh_market_info("BATS"))

# Get the market hours.
str(rh_market_hours("BATS"))

```

### Instruments

Use rh_instruments to get a data.frame of all the available symbols. The API results are paginated, so it will a minute to download. You can also search and get fundamentals for a stock.

```{r instruments}
## Get a data.frame of all the instruments.
str(rh_instruments())

# Seach for a specific keyword
str(rh_instruments_search(keyword = "oil"))

# Get fundamentals for a symbol
str(rh_instruments_info(symbols = symbols))

```

### Related Projects

- [Python](https://github.com/MeheLLC/Robinhood) 
- [npmjs](https://www.npmjs.com/package/robinhood)
- [chris Busse Notes](http://chrisbusse.com/research/robinhood-brokerage-api-notes.html)




